### 2015-02-03 paper_20_sdo.tex
increased image size

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/benington_waterfall.PNG}
            \caption[BENINGTON'S ORIGINAL DIAGRAM FOR PRODUCING LARGE SOFTWARE SYSTEMS]
                    {Benington's original diagram for producing large software 
                        systems, adapted from \cite{Benington1987}}
            \label{fig:benington}
        \end{figure}%
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.5]{images/royce_waterfall.PNG}
            \caption[ROYCE'S VERSION OF THE WATERFALL MODEL]
                {Royce's version of the waterfall model for producing software 
                        systems, adapted from \cite{Royce1987}}
            \label{fig:royce}
        \end{figure}

        The modern version of the waterfall model specifies that each phase needs 
        to be entirely completed before moving
        onto the next phase.  Some small amount of overlap is permitted and looping 
        occurs but both actions are discouraged and should be limited.  
        A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.6]{images/waterfall.png}
            \caption[MODERN WATERFALL]
                {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
            \label{fig:waterfall}
        \end{figure}

@@

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral model of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.5]{images/spiral_model.png}
            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

@@

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        there is still some commonalities among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the Implemenation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a roadmap for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development lifecycle.
        \end{description}

>>>>

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.7]{images/benington_waterfall.PNG}
            \caption[BENINGTON'S ORIGINAL DIAGRAM FOR PRODUCING LARGE SOFTWARE SYSTEMS]
                    {Benington's original diagram for producing large software 
                        systems, adapted from \cite{Benington1987}}
            \label{fig:benington}
        \end{figure}%
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.7]{images/royce_waterfall.PNG}
            \caption[ROYCE'S VERSION OF THE WATERFALL MODEL]
                {Royce's version of the waterfall model for producing software 
                        systems, adapted from \cite{Royce1987}}
            \label{fig:royce}
        \end{figure}

        The modern version of the waterfall model specifies that each phase needs 
        to be entirely completed before moving
        onto the next phase.  Some small amount of overlap is permitted and looping 
        occurs but both actions are discouraged and should be limited.  
        A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.9]{images/waterfall.png}
            \caption[MODERN WATERFALL]
                {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
            \label{fig:waterfall}
        \end{figure}

@@

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral model of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.8]{images/spiral_model.png}
            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

@@

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        many ommonalities exist among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the Implemenation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a roadmap for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development lifecycle.
        \end{description}
